### 2021-01-15 publications/2020-03-paper/Appendix.tex
adds kdh corretions, glossaries, CRediT statement
Former-commit-id: 63eaba071d907d33887c9080bc221f79aae32636
Former-commit-id: 1b7ddd720025f2dbe7f1ec4b96fdcca1d1df9dd9
table width corrections
Former-commit-id: a4ff51e31bd544a52a096e930ca445bf82b93850
Former-commit-id: 09643fa16296f68238b830398d495eeb626abb69

\begin{table}[H]
	\caption{Initial condition for CO$_2$ emissions compared with data from the Carbon Trust\cite{carbon_brief_carbon_2018}.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.08\textwidth} p{0.35\textwidth} p{0.35\textwidth} p{0.15\textwidth}}
\textbf{Year} & \textbf{Model emissions} & \textbf{Actual emissions} & \textbf{Error} \\
  & (Mt CO$_2$-eq.) & (Mt CO$_2$-eq.) &  \\
2013 & 603.62 & 592.4 & 1.89 \% \\
2014 & 582.27 & 572.6 & 1.69 \% \\
2015 & 572.53 & 560.3 & 2.18 \% \\
2016 & 565.94 & 552.8 & 2.38 \% \\
	\end{tabularx}
\label{ic-co2}
\end{table}

@@

Li-ion storage \cite{mongird_energy_2019,emilsson_lithium-ion_2019} & 1876 (2017) & 10 & 0.3 & 10 & Eff=0.86 & 151(2017) & 2017 \\

>>>>

\begin{table}[H]
	\caption{Initial condition for CO$_2$ emissions compared with data from the Carbon Trust\cite{carbon_brief_carbon_2018}.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.08\textwidth} p{0.35\textwidth} p{0.35\textwidth} p{0.15\textwidth}}
		\hline
\textbf{Year} & \textbf{Model emissions} & \textbf{Actual emissions} & \textbf{Error} \\
  & (Mt CO$_2$-eq.) & (Mt CO$_2$-eq.) &  \\
\hline
2013 & 603.62 & 592.4 & 1.89 \% \\
2014 & 582.27 & 572.6 & 1.69 \% \\
2015 & 572.53 & 560.3 & 2.18 \% \\
2016 & 565.94 & 552.8 & 2.38 \% \\
\hline 
	\end{tabularx}
\label{ic-co2}
\end{table}

@@

Li-ion storage \cite{mongird_energy_2019,emilsson_lithium-ion_2019,oliveira_environmental_2015} & 1876 (2017) & 10 & 0.3 & 10 & Eff=0.86 & 151(2017) & 2017 \\

### 2021-01-15 publications/2020-03-paper/methods.tex
table width corrections
Former-commit-id: a4ff51e31bd544a52a096e930ca445bf82b93850
Former-commit-id: 09643fa16296f68238b830398d495eeb626abb69

\begin{table}[!ht]
	\caption{Electricity demand increase over the simulation time frame.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.5\textwidth} p{0.5\textwidth}}
		\hline
\textbf{Year} & \textbf{Annual demand increase} \\
\hline
2017-2030 & 1.7 \% \cite{noauthor_electricity_2019} \\
2031-2050 & 1.0 \% \\
2051-2070 & 0.5 \% \\
2070-2100 & 0.0 \% \\
\hline 
	\end{tabularx}
\label{demand}
\end{table}

\begin{table}[!ht]
	\caption{Emission constraints.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.1\textwidth} p{0.22\textwidth}p{0.16\textwidth} p{0.4\textwidth}}
		\hline
\textbf{Year} & \textbf{Emission limit} & \textbf{Base year} & \textbf{Reduction from base year} \\
\hline
2030 & 438 Mt CO$_2$-eq. & 2013 & 26 \% \\
2050 & 75 Mt CO$_2$-eq. & 1990 & 80 \% \\
2100 & 75 Mt CO$_2$-eq. & 2050 & 0 \% \\
\hline 
	\end{tabularx}
\label{co2-limits}
\end{table}

@@

\begin{table}[!ht]
	\caption{Electricity supply transition scenario definition.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.15\textwidth} p{0.25\textwidth} p{0.25\textwidth} p{0.35\textwidth}}
\hline 
\textbf{Scenario}& \textbf{Emerging tech.} & \textbf{New nuclear} & \textbf{Nascent tech.}\\
                 & \textbf{enabled} & \textbf{enabled} & \textbf{enabled}\\
                  \hline
%1               &   \xmark       &      \greencheck     \\ 
%2               & \xmark       &         \xmark       \\ 
%3               &   \greencheck     &      \greencheck     \\ 
%4               &   \greencheck     &         \xmark       \\
1               &  No       &         No     &     No  \\ 
2               &   No       &      Yes     &     No  \\ 
3               &   Yes     &         No      &     No   \\
4               &   Yes     &      Yes     &     No  \\ 
5               &   Yes     &      No     &     Yes  \\ 
\hline
	\end{tabularx}
\label{scen-table}
\end{table}

@@

\begin{table}[!ht]
	\caption{Candidate parameters and their variation in our sensitivity analysis.}
	\vspace{0.1in}
	\begin{tabularx}{1.1\textwidth}{p{0.3\textwidth} p{0.25\textwidth} p{0.25\textwidth}p{0.3\textwidth}}
\hline 
\textbf{Technology}  & \textbf{Sampled} & \textbf{Distribution}& \textbf{Distribution}\\
\textbf{Parameter} & \textbf{Distribution} & \textbf{Mean}& \textbf{Range}\\
\hline
\gls{PWS} Investment Cost       & Gaussian    & 3088 \$/kW & $\pm$20\% of mean. \\                  
\gls{SOEC} Investment Cost      & Gaussian    & 1388 \$/kW & $\pm$20\% of mean.\\                  
\gls{PEMEC} Investment Cost     & Gaussian    & 3800 \$/kW & $\pm$20\% of mean.\\                  
\gls{SOFC} Investment Cost      & Gaussian    & 7399 \$/kW & $\pm$20\% of mean.\\                  
\gls{PEMFC} Investment Cost     & Gaussian    & 7399 \$/kW & $\pm$20\% of mean.\\                  
\gls{CCS} Gas Investment Cost   & Gaussian    & 2626 \$/kW & $\pm$20\% of mean.\\                  
\gls{CCS} Coal Investment Cost  & Gaussian    & 5252 \$/kW & $\pm$20\% of mean.\\
\gls{PWS} Emission Coefficient  & Triangular  & 1.08 g/kWh & 0.2-5.405 g/kWh. \\                  
\gls{SOEC} Emission Coefficient & Triangular  & 1.08 g/kWh & 0.2-5.405 g/kWh. \\
\gls{PWS} Efficiency            & Triangular  & 0.525 & 0.5-0.58. \\                               
\hline
	\end{tabularx}
\label{sa-vars}
\end{table}

>>>>

\begin{table}[!ht]
	\caption{Electricity demand increase over the simulation time frame.}
	\vspace{0.1in}
	\begin{tabularx}{0.4\textwidth}{p{0.15\textwidth} p{0.25\textwidth}}
		\hline
\textbf{Year} & \textbf{Annual demand} \\
 & \textbf{increase} \\
\hline
2017-2030 & 1.7 \% \cite{noauthor_electricity_2019} \\
2031-2050 & 1.0 \% \\
2051-2070 & 0.5 \% \\
2070-2100 & 0.0 \% \\
\hline 
	\end{tabularx}
\label{demand}
\end{table}

\begin{table}[!ht]
	\caption{Emission constraints.}
	\vspace{0.1in}
	\begin{tabularx}{0.6\textwidth}{p{0.05\textwidth} p{0.2\textwidth}p{0.05\textwidth} p{0.3\textwidth}}
		\hline
\textbf{Year} & \textbf{Emission limit} & \textbf{Base} & \textbf{Reduction} \\
 & & \textbf{year} & \textbf{from base year} \\
\hline
2030 & 438 Mt CO$_2$-eq. & 2013 & 26 \% \\
2050 & 75 Mt CO$_2$-eq. & 1990 & 80 \% \\
2100 & 75 Mt CO$_2$-eq. & 2050 & 0 \% \\
\hline 
	\end{tabularx}
\label{co2-limits}
\end{table}

@@

\begin{table}[!ht]
	\caption{Electricity supply transition scenario definition based on enabled technologies.}
	\vspace{0.1in}
	\begin{tabularx}{0.65\textwidth}{p{0.1\textwidth} p{0.18\textwidth} p{0.15\textwidth} p{0.18\textwidth}}
\hline 
\textbf{Scenario}& \textbf{Emerging} & \textbf{New} & \textbf{Nascent}\\
 & \textbf{tech.} & \textbf{nuclear} & \textbf{tech.}\\

%                 & \textbf{enabled} & \textbf{enabled} & \textbf{enabled}\\
                  \hline
%1               &   \xmark       &      \xmark     &   \xmark     \\ 
%2               &   \xmark       &      \greencheck     &   \xmark     \\ 
%3               &   \greencheck       &      \xmark     &   \xmark     \\ 
%4               &   \greencheck       &      \greencheck     &   \xmark     \\ 
%5               &   \greencheck       &      \xmark     &   \greencheck     \\ 
1               &  No       &         No     &     No  \\ 
2               &   No       &      Yes     &     No  \\ 
3               &   Yes     &         No      &     No   \\
4               &   Yes     &      Yes     &     No  \\ 
5               &   Yes     &      No     &     Yes  \\ 
\hline
	\end{tabularx}
\label{scen-table}
\end{table}

@@

\begin{table}[!ht]
	\caption{Candidate parameters and their variation in our sensitivity analysis.}
	\vspace{0.1in}
	\begin{tabularx}{0.9\textwidth}{p{0.3\textwidth} p{0.15\textwidth} p{0.15\textwidth}p{0.3\textwidth}}
\hline 
\textbf{Technology}  & \textbf{Sampled} & \textbf{Distribution}& \textbf{Distribution}\\
\textbf{Parameter} & \textbf{Distribution} & \textbf{Mean}& \textbf{Range}\\
\hline
\gls{PWS} Investment Cost       & Gaussian    & 3088 \$/kW & $\pm$20\% of mean. \\                  
\gls{SOEC} Investment Cost      & Gaussian    & 1388 \$/kW & $\pm$20\% of mean.\\                  
\gls{PEMEC} Investment Cost     & Gaussian    & 3800 \$/kW & $\pm$20\% of mean.\\                  
\gls{SOFC} Investment Cost      & Gaussian    & 7399 \$/kW & $\pm$20\% of mean.\\                  
\gls{PEMFC} Investment Cost     & Gaussian    & 7399 \$/kW & $\pm$20\% of mean.\\                  
\gls{CCS} Gas Investment Cost   & Gaussian    & 2626 \$/kW & $\pm$20\% of mean.\\                  
\gls{CCS} Coal Investment Cost  & Gaussian    & 5252 \$/kW & $\pm$20\% of mean.\\
\gls{PWS} Emission Coefficient  & Triangular  & 1.08 g/kWh & 0.2-5.405 g/kWh. \\                  
\gls{SOEC} Emission Coefficient & Triangular  & 1.08 g/kWh & 0.2-5.405 g/kWh. \\
\gls{PWS} Efficiency            & Triangular  & 0.525 & 0.5-0.58. \\                               
\hline
	\end{tabularx}
\label{sa-vars}
\end{table}

### 2021-01-15 publications/2020-03-paper/results.tex
adds kdh corretions, glossaries, CRediT statement
Former-commit-id: 63eaba071d907d33887c9080bc221f79aae32636
Former-commit-id: 1b7ddd720025f2dbe7f1ec4b96fdcca1d1df9dd9
table width corrections
Former-commit-id: a4ff51e31bd544a52a096e930ca445bf82b93850
Former-commit-id: 09643fa16296f68238b830398d495eeb626abb69

@@

@@

The results of each scenario (Table \ref{scen-table} for scenario definitions) are reported as annually aggregated plots of (i) the electricity that is directly supplied to the end user, (ii) the active nameplate capacities of generation and storage technologies, and (iii) the resulting emissions (direct and life cycle) from each technology. The first plot of each scenario shows a large degree of variation as generated electricity is diverted from multiple sources to storage technologies instead of being supplied directly to the end user. The output of some technologies also varies due to their ability to load-follow. The second plot describes the transitions in terms of capacities, highlighting the effect of the capacity factor of intermittent versus base-load technologies. The third plot details the sources of direct and averaged life-cycle emissions from each source.

The fifth scenario's results (Figure \ref{scen5}) closely resemble those of the third scenario (Figure \ref{scen3}). However, \gls{SOEC}s rapidly replace a large fraction of aging \gls{PEMEC}s, starting from 2055. Some \gls{PEMEC}s remain in the mix until 2100 despite their lower efficiency due to their lower cost. Both 2030 and 2050 emission targets are met, but no additional emission reductions occur beyond 2050. The amount of electricity diverted to storage technologies is 41,752 TWh, primarily from solar and emerging solar technologies (48\%), onshore wind (28\%), and fixed-bottom offshore wind (20\%). From this, 35,550 TWh of hydrogen is generated, mostly from \gls{SOEC} (56\%), and \gls{PEMEC} (43\%). \gls{AEC} contributes a mere 0.95\% of the total hydrogen, and \gls{PWS} plays the smallest role at 0.05\%. The cost of this transition is \textbf{3.18 trillion USD}.

>>>>

The transition simulations' results are shown in Figures \ref{scen1}-\ref{scen5}, and summarised in Table \ref{tab:results_summary} (see Table \ref{scen-table} for scenario definitions). The results of each scenario are reported as annually aggregated plots of (i) the electricity that is directly supplied to the end user, (ii) the active nameplate capacities of generation and storage technologies, and (iii) the resulting emissions (direct and life cycle) from each technology. The first plot of each scenario shows a large degree of variation as generated electricity is diverted from multiple sources to storage technologies instead of being supplied directly to the end user. The output of some technologies also varies due to their ability to load-follow. The second plot describes the transitions in terms of capacities, highlighting the effect of the capacity factor of intermittent versus base-load technologies. The third plot details the sources of direct and averaged life-cycle emissions from each source.

\begin{table}[!ht]
	\caption{Summary of decarbonisation simulations' results.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.1\textwidth} p{0.2\textwidth}p{0.1\textwidth}p{0.1\textwidth}p{0.2\textwidth}p{0.2\textwidth}}
		\hline
\textbf{Scenario} & \textbf{Enabled} & \textbf{Meets} & \textbf{Meets} & \textbf{Emissions} & \textbf{Cost} \\
 & \textbf{Technologies} & \textbf{2030} & \textbf{2050} & \textbf{between} & (USD 2015) \\
 &  & \textbf{emission} & \textbf{emission} & \textbf{2050-2100} &  \\
 &  & \textbf{goals} & \textbf{goals} & &  \\
\hline
1 & Conventional tech., no new nuclear & Yes & No & +25 Mt & 3.51 trillion. \\
2 & Conventional tech., with new nuclear & Yes & Yes & -12 Mt & 2.66 trillion. \\
3 & Emerging tech., no new nuclear & Yes & Yes & No change & 3.19 trillion. \\
4 & Emerging tech., with new nuclear & Yes & Yes & -32 Mt & 2.80 trillion. \\
5 & Nascent tech., no new nuclear & Yes & Yes & No change & 3.18 trillion. \\
\hline 
	\end{tabularx}
\label{tab:results_summary}
\end{table}

@@

The fifth scenario's results (Figure \ref{scen5}) closely resemble those of the third scenario (Figure \ref{scen3}). However, \gls{SOEC}s rapidly replace a large fraction of ageing \gls{PEMEC}s, starting from 2055. Some \gls{PEMEC}s remain in the mix until 2100 despite their lower efficiency due to their lower cost. Both 2030 and 2050 emission targets are met, but no additional emission reductions occur beyond 2050. The amount of electricity diverted to storage technologies is 41,752 TWh, primarily from solar and emerging solar technologies (48\%), onshore wind (28\%), and fixed-bottom offshore wind (20\%). From this, 35,550 TWh of hydrogen is generated, mostly from \gls{SOEC} (56\%), and \gls{PEMEC} (43\%). \gls{AEC} contributes a mere 0.95\% of the total hydrogen, and \gls{PWS} plays the smallest role at 0.05\%. The cost of this transition is \textbf{3.18 trillion USD}.

@@
